---
title: "MT5000 Quarto Assignment"
author: "Kiran Vargaonkar"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# <span style="background-color:#0066B3; color:#FFFFFF; padding:5px;">SDG 2.2.2: Prevalence of Malnutrition Among Children aged 2 to 3 Years</span>

- <span style="color:#0066B3;">Malnourished children, particularly those with severe acute malnutrition, have a higher risk of death from common childhood illness such as diarrhoea, pneumonia, and malaria. Nutrition-related factors contribute to about 45% of deaths in children under-5 years of age.</span>

- <span style="color:#0066B3;">In 2020, 22 per cent, or more than one in five children under age 5 worldwide had stunted growth.</span>

- <span style="color:#0066B3;">Around 149 million children under the age of 5 were stunted (too short for their age) due to malnutrition in 2020.</span>

- <span style="color:#0066B3;">In 2020, about 45 million children were wasted (too thin for their height) due to acute malnutrition.</span>


```{r echo=FALSE, ,message=FALSE}
library(shiny)
library(dplyr)
library(ggplot2)
library(readr)

```


### <span style="background-color:#0066B3; color:#FFFFFF; padding:5px;">Visualize BMI Trends Across the World

```{r echo=FALSE, message=FALSE, warning=FALSE}
source("world_map.R")
```

### <span style="background-color:#0066B3; color:#FFFFFF; padding:5px;">Average BMI value according to gender

```{r echo=FALSE}
source("bar_chart.R")
```

### <span style="background-color:#0066B3; color:#FFFFFF; padding:5px;">Observed BMI value by year

```{r echo=FALSE, message=FALSE, warning=FALSE}
source("scatter.R")
```

### <span style="background-color:#0066B3; color:#FFFFFF; padding:5px;">Long-Term Trends in BMI for Children Aged 2-3 Years: 2001-2020

```{r echo=FALSE}
source("time_series.R")
```

